Influences of GDP in the U.S

### 2022-11-14 Manuscript/manuscript.tex
commit

The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S. Energy Information Administration website. 
The EIA "collects, analyzes, and disseminates independent and impartial energy information to promote sound policymaking, efficient markets, and public understanding of energy and its interaction with the economy and the environment."\citet[]{eia}.

>>>>

The variable Total Primary Energy Consumption (Quadrillion Btu) used in this research was collected from the U.S. Energy Information Administration website. 
The EIA collects and analyzes data to promote energy information. Their goal is to promote effective policy decisions, efficient markets, and to increase the public's understanding of energy and its influence on the economy.
